Joint modelling

### 2020-11-22 manuscript/hmm.Rmd
Jm and risks for supplement

if(length(unique(data$patient_data$patient_id)) != length(data$patient_data$patient_id)) {
  stop("FAil")
}
# warning("Subsetting data")
# set.seed(4568224)
# patients_to_use <- sample(data$patient_data$patient_id, size = 70)
# data <- filter_complete_data(data, patient_id %in% patients_to_use)

>>>>

if(length(unique(data$patient_data$patient_id)) != length(data$patient_data$patient_id)) {
  stop("FAil")
}

### 2020-11-22 manuscript/jm.Rmd
Jm and risks for supplement

---
title: "Joint modelling"
output: html_notebook
---

@@

```{r}
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[1:11])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[12:14])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[15:18])
plot(p1, plot_observed = TRUE)

p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[19:20])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[21:22])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[22:26])
plot(p1, plot_observed = TRUE)
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[27:29])
plot(p1, plot_observed = TRUE)                     
p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[30:32])
plot(p1, plot_observed = TRUE)                     
```

>>>>

---
title: "Joint modelling"
output: html_document
---

# Joint longitudinal and time-to-event models

@@

```{r}
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[1:11])
# plot(p1, plot_observed = TRUE)                     
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[12:14])
# plot(p1, plot_observed = TRUE)                     
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[15:18])
# plot(p1, plot_observed = TRUE)                     
# 
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[19:20])
# plot(p1, plot_observed = TRUE)                     
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[21:22])
# plot(p1, plot_observed = TRUE)                     
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[22:26])
# plot(p1, plot_observed = TRUE)
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[27:29])
# plot(p1, plot_observed = TRUE)                     
# p1 <- posterior_traj(fit_d_dimer_age_sex_hcq, ids = unique(data_d_dimer$patient_id)[30:32])
# plot(p1, plot_observed = TRUE)                     
```
